---
title: "temporary"
output: html_document
date: "2023-08-21"
---

```{r setup, include=FALSE}
library(tidyverse)
require(ggplot2)
require(MASS)
require(Hmisc)
require(reshape2)
library(forcats)
library(effects)
library(splines)
library(car)
library(VGAM)
library(foreign)
library(plotly)
library(patchwork)
```

# Clean data
## Load data
```{r}
dat <- readxl::read_xlsx("/Volumes/manhnd/Yi_roe_data.xlsx")
# filter variables for analyis
dat <- dat %>% dplyr::select("serialno", "country", "papm", "gender", "age", "education", "marital", "occupation", "live_area", "mobile", "internet")
```

## Transform data
```{r}
# Remove the gender as others (18/2912)
dat1 <- dat %>%
  filter(gender != 3 & gender != 4) %>%
  mutate(marital = dplyr::recode(marital, `4` = 3, `5` = 3))

# Transform the valuables
dat1 <- dat1 %>%
  mutate(
    papm = factor(papm, ordered = TRUE),
    gender = factor(gender, labels = c("Male", "Female")),
    marital = factor(marital, labels = c("Never married", "Married/living with a partner", "Separated/widowed/divorced")),
    education = factor(education, labels = c("No formal education", "Primary school", "Secondary school", "Diploma", "Degree")),
    occupation = factor(occupation, labels = c("Employed", "Unemployed", "Student", "Retiree", "Homemaker")),
    live_area = factor(live_area, labels = c("Urban", "Peri-urban", "Rural", "Slums")),
    mobile = factor(mobile, labels = c("No", "Yes feature phone", "Yes smart phone")),
    internet = factor(internet, labels = c("No", "Yes")),
    country = factor(country)
  ) %>%
  mutate(
    education = fct_relevel(education, "Degree", "Diploma", "Secondary school", "Primary school", "No formal education")
  )


summary(dat1)
str(dat1)
```

## Visualize some variables
### papm versus countries
```{r, fig.width = 10}
# keep participant with gender as other
# dat1 <- dat %>%
#   mutate(gender = dplyr::recode(gender, `4` = 3)) %>%
#   mutate(marital = dplyr::recode(marital, `4` = 3, `5` = 3))
#
# # Transform the valuables
# dat1 <- dat1 %>%
#   mutate(
#     papm = factor(papm, ordered = TRUE),
#     gender = factor(gender, labels = c("Male", "Female", "Other")),
#     marital = factor(marital, labels = c("Never married", "Married/living with a partner", "Separated/widowed/divorced")),
#     education = factor(education, labels = c("No formal education", "Primary school", "Secondary school", "Diploma", "Degree")),
#     occupation = factor(occupation, labels = c("Employed", "Unemployed", "Student", "Retiree", "Homemaker")),
#     live_area = factor(live_area, labels = c("Urban", "Peri-urban", "Rural", "Slums")),
#     mobile = factor(mobile, labels = c("No", "Yes feature phone", "Yes smart phone")),
#     internet = factor(internet, labels = c("No", "Yes")),
#     country = factor(country)
#   ) %>%
#   mutate(
#     education = fct_relevel(education, "Degree", "Diploma", "Secondary school", "Primary school", "No formal education"),
#     mobile = fct_relevel(mobile, "Yes smart phone", "Yes feature phone", "No")
#   )

dat2 <- dat1 %>%
  select("country", "papm") %>%
  group_by(country, papm) %>%
  summarise(n = n()) %>%
  mutate(proportion_papm = round(n / sum(n) * 100, 2)) %>%
  ungroup() %>%
  mutate(papm = factor(papm, labels = c(
    "Unaware", "Aware but unengaged", "Aware, engaged, \nbut undecided",
    "Aware, engaged, decided, \nbut yet to take action", "Aware, engaged, decided, \ntook action"
  )))

max <- dat2 %>%
  group_by(country) %>%
  slice(which.max(proportion_papm))

ggplot(data = dat2, aes(x = country, y = proportion_papm, fill = papm)) +
  geom_col(width = 0.5) +
  geom_text(data = max, aes(label = proportion_papm)) +
  facet_grid(~papm) +
  coord_flip(ylim = c(0, 100)) +
  scale_fill_brewer(direction = 1, palette = "YlOrRd") + # YlOrRd
  labs(x = "Country", y = "Proportion (%)") +
  theme(legend.position = "none")
```

### Education versus countries
```{r}
dat2 <- dat %>%
  select("country", "education") %>%
  group_by(country, education) %>%
  summarise(n = n()) %>%
  mutate(proportion_education = n / sum(n)) %>%
  ungroup()

ggplot(data = dat2, aes(x = country, y = proportion_education)) +
  geom_col(width = 0.5) +
  facet_grid(~education) +
  coord_flip()
```

# MASS package: polr modell
## Fit the modell without country interaction

```{r echo=T, results='hide'}
m1 <- polr(formula = papm ~ country + gender + age + education + marital + occupation + live_area + mobile + internet, data = dat1, Hess = TRUE)

summary(m1)
```

## Fit the model with country interaction

```{r echo=T, results='hide'}
# First fit the model with interaction between country and all of the independent variables but the model cannot run. Then I removed the interaction between live_area and country, model can run as below
m2 <- polr(formula = papm ~ country + gender + age + education + marital + occupation + live_area + mobile + internet + gender:country + age:country + marital:country + occupation:country + mobile:country + internet:country + education:country, data = dat1, Hess = TRUE)

summary(m2)
# compare with model 1
anova(m1, m2, test = "Chisq")
Anova(m2)
# m2 is beter than m1.
```

## Obtain the confident interval
I use Wald test to obtain the CI because the likelihood ratio test doesn't work

```{r}
countryList <- c("Bangladesh", "Cameroon", "India", "Indonesia", "Kenya", "Nepal", "Philippines", "Uganda", "Zimbabwe")

func_obtainCI <- function(data, countryList) {
  allData <- list()

  for (ctry in countryList) {
    m <- polr(formula = papm ~ gender + age + education + marital + occupation + live_area + mobile + internet, data = data %>% filter(country == ctry), Hess = TRUE)

    ci <- confint.default(m)

    tmp <- as.data.frame(round(exp(cbind(OR = coef(m), ci)), 2)) %>%
      mutate(
        country = ctry,
        predictor = row.names(m)
      )

    allData[[ctry]] <- tmp
  }

  combinedData <- do.call(rbind, allData)

  return(combinedData)
}


tmpCI <- func_obtainCI(dat1, countryList)

# Generate data frame
# tmpCI1 <- tmpCI %>%
#   mutate(independent_var = row.names(tmpCI)) %>%
#   separate(independent_var, c("count", "var"), sep = "\\.") %>%
#   mutate(var = str_replace_all(var, c(
#     "gender" = "gender.",
#     "age" = "age.Age",
#     "education" = "education.",
#     "marital" = "marital.",
#     "occupation" = "occupation.",
#     "live_area" = "live_area.",
#     "mobile" = "mobile.",
#     "internet" = "internet."
#   ))) %>%
#   separate(var, c("independent_variable", "value"), "\\.")%>%
#   mutate(reference = str_replace_all(independent_variable, c(
#     "gender" = "Male",
#     "age" = "Continuous",
#     "education" = "Degree",
#     "marital" = "Never married",
#     "occupation" = "Employed",
#     "live_area" = "Urban",
#     "mobile" = "No",
#     "internet" = "No")))%>%
#   select("country", "independent_variable", "reference", "value", "OR", `2.5 %`, `97.5 %`)
#
# writexl::write_xlsx(tmpCI1, "~/Downloads/20230825tmp_01.xlsx")
```
## Visualize the result
### Clean the result
```{r}
tmp1 <- tmpCI %>%
  mutate(independent_var = row.names(tmpCI)) %>%
  separate(independent_var, c("count", "var"), sep = "\\.") %>%
  mutate(var = str_replace_all(var, c(
    "gender" = "gender.",
    "age" = "age.Continuous",
    "education" = "education.",
    "marital" = "marital.",
    "occupation" = "occupation.",
    "live_area" = "live_area.",
    "mobile" = "mobile.",
    "internet" = "internet."
  ))) %>%
  separate(var, c("var", "level"), "\\.") %>%
  mutate(
    OR = ifelse(OR >= 1000, 0, OR),
    `2.5 %` = ifelse(`2.5 %` >= 1000, 0, `2.5 %`),
    `97.5 %` = ifelse(`97.5 %` >= 1000, 0, `97.5 %`)
  )
```
### Gender
```{r}
tmp2 <- tmp1 %>%
  filter(var == "gender")

p1 <- ggplot(data = tmp2, aes(x = level, y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.3), width = 0.25) +
  geom_point(size = 2, position = position_dodge(0.3)) +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Gender-Male", x = "") +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank()
  )
```
### Age
```{r}
tmp2 <- tmp1 %>%
  filter(var == "age") %>%
  mutate(level = as.factor(level))

p2 <- ggplot(data = tmp2, aes(x = level, y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.3), width = 0.25) +
  geom_point(size = 2, position = position_dodge(0.3)) +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Age", x = "", y = "") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank()
  )
```
### Education
```{r}
tmp2 <- tmp1 %>%
  filter(var == "education") %>%
  mutate(level = as.factor(level)) %>%
  mutate(level = fct_relevel(level, "No formal education", "Primary school", "Secondary school", "Diploma"))

p3 <- ggplot(data = tmp2, aes(x = level, y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.85), width = 1) +
  geom_point(size = 2, position = position_dodge(0.85)) +
  geom_vline(xintercept = seq(1.5, 3.5, by = 1), colour = "grey", linetype = "dashed") +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Education-Degree", x = "", y = "") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid.major.x = element_blank()
  )
```
### Marital
```{r}
tmp2 <- tmp1 %>%
  filter(var == "marital") %>%
  mutate(level = as.factor(level))

p4 <- ggplot(data = tmp2, aes(x = level, y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.6), width = 0.5) +
  geom_point(size = 2, position = position_dodge(0.6)) +
  geom_vline(xintercept = 1.5, colour = "grey", linetype = "dashed") +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Marital-Never married", x = "", y = "") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid.major.x = element_blank()
  )
```
### Occupation
```{r}
tmp2 <- tmp1 %>%
  filter(var == "occupation") %>%
  mutate(level = as.factor(level))

p5 <- ggplot(data = tmp2, aes(x = level, y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.85), width = 1) +
  geom_point(size = 2, position = position_dodge(0.85)) +
  geom_vline(xintercept = seq(1.5, 3.5, by = 1), colour = "grey", linetype = "dashed") +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Occupation-Employed", x = "") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid.major.x = element_blank()
  )
```
### Live area
```{r}
tmp2 <- tmp1 %>%
  filter(var == "live_area") %>%
  mutate(level = as.factor(level))

p6 <- ggplot(data = tmp2, aes(x = level, y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.7), width = 0.5) +
  geom_point(size = 2, position = position_dodge(0.7)) +
  geom_vline(xintercept = seq(1.5, 2.5, by = 1), colour = "grey", linetype = "dashed") +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Live area-Urban", x = "", y = "") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid.major.x = element_blank()
  )
```
### Mobile
```{r}
tmp2 <- tmp1 %>%
  filter(var == "mobile") %>%
  mutate(level = as.factor(level))

p7 <- ggplot(data = tmp2, aes(x = fct_inorder(level), y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.6), width = 0.5) +
  geom_point(size = 2, position = position_dodge(0.6)) +
  geom_vline(xintercept = 1.5, colour = "grey", linetype = "dashed") +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Mobile-Yes smart phone", x = "", y = "") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid.major.x = element_blank()
  )
```
### Internet
```{r}
tmp2 <- tmp1 %>%
  filter(var == "internet") %>%
  mutate(level = as.factor(level))

p8 <- ggplot(data = tmp2, aes(x = level, y = OR, colour = country)) +
  geom_hline(yintercept = 1, colour = "black") +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`), position = position_dodge(0.3), width = 0.25) +
  geom_point(size = 2, position = position_dodge(0.3)) +
  scale_y_continuous(trans = "log10") +
  scale_colour_brewer(palette = "Set1") +
  labs(title = "Internet-No", x = "", y = "") +
  theme(panel.grid.major.x = element_blank())
```


```{r, warning=FALSE, fig.width = 10, fig.height=7}
(p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 +
  plot_layout(ncol = 4, guides = "collect"))
```

## Obtain P value for each independent variable for individual country
We can use anova() function to obtain the P value for each independent variable using likeli-hood ratio test

```{r, warning= FALSE}
func_obtainP <- function(data, countryList) {
  allData <- list()

  for (ctry in countryList) {
    dat <- data %>% filter(country == ctry)
    m <- polr(formula = papm ~ gender + age + education + marital + occupation + live_area + mobile + internet, data = dat, Hess = TRUE)
    m1 <- polr(formula = papm ~ age + education + marital + occupation + live_area + mobile + internet, data = dat, Hess = TRUE)
    m2 <- polr(formula = papm ~ gender + education + marital + occupation + live_area + mobile + internet, data = dat, Hess = TRUE)
    m3 <- polr(formula = papm ~ gender + age + marital + occupation + live_area + mobile + internet, data = dat, Hess = TRUE)
    m4 <- polr(formula = papm ~ gender + age + education + occupation + live_area + mobile + internet, data = dat, Hess = TRUE)
    m5 <- polr(formula = papm ~ gender + age + education + marital + live_area + mobile + internet, data = dat, Hess = TRUE)
    m6 <- polr(formula = papm ~ gender + age + education + marital + occupation + mobile + internet, data = dat, Hess = TRUE)
    m7 <- polr(formula = papm ~ gender + age + education + marital + occupation + live_area + internet, data = dat, Hess = TRUE)
    m8 <- polr(formula = papm ~ gender + age + education + marital + occupation + live_area + mobile, data = dat, Hess = TRUE)

    tmp1 <- anova(m, m1)
    tmp2 <- anova(m, m2)
    tmp3 <- anova(m, m3)
    tmp4 <- anova(m, m4)
    tmp5 <- anova(m, m5)
    tmp6 <- anova(m, m6)
    tmp7 <- anova(m, m7)
    tmp8 <- anova(m, m8)

    tmp <- bind_rows(list(tmp1, tmp2, tmp3, tmp4, tmp5, tmp6, tmp7, tmp8)) %>%
      filter(!is.na(`Pr(Chi)`)) %>%
      select(`Pr(Chi)`) %>%
      mutate(
        var = c("gender", "age", "education", "marital", "occupation", "live_area", "mobile", "internet"),
        country = ctry,
        `Pr(Chi)` = round(`Pr(Chi)`, 4)
      )

    allData[[ctry]] <- tmp
  }

  combinedData <- do.call(rbind, allData)

  return(combinedData)
}


tmpP <- func_obtainP(dat1, countryList)
tmpP1 <- tmpP %>%
  mutate(
    level = "",
    OR = NA,
    `2.5 %` = NA,
    `97.5 %` = NA
  ) %>%
  select("country", "var", "level", "OR", "2.5 %", "97.5 %", "Pr(Chi)")

tmp2 <- tmp1 %>%
  select("country", "var", "level", "OR", "2.5 %", "97.5 %") %>%
  mutate(`Pr(Chi)` = NA)
combine <- bind_rows(tmpP1, tmp2) %>%
  arrange(country, var)
#writexl::write_xlsx(combine, "~/Downloads/20230828tmp.xlsx")
```
